---
title       : Wine Quality
subtitle    : Modeling wine preferences to match human taste
author      : Christian Sousa
job         :
framework   : io2012          # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js    # {highlight.js, prettify, highlight}
hitheme     : tomorrow_night  #
widgets     : []              # {mathjax, quiz, bootstrap}
mode        : selfcontained   # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

The wine quality datasets used for this presentation were taken from the UCI datasets.

https://archive.ics.uci.edu/ml/datasets/Wine+Quality

The companion article to the datasets proposed a data mining approach to predict the human wine taste preferences.

http://www.sciencedirect.com/science/article/pii/S0167923609001377

--- .class #id

## Datasets description

- Red wine (only 4 rows and 3 predictors are shown)

```{r, echo = FALSE, eval = TRUE}
wine <- read.csv('winequality-red.csv', header = TRUE, sep = ";")
head(wine[c("volatile.acidity", "pH", "alcohol", "quality")], 4)
```

- White wine (only 4 rows and 3 predictors are shown)

```{r, echo = FALSE, eval = TRUE}
wine <- read.csv('winequality-white.csv', header = TRUE, sep = ";")
head(wine[c("volatile.acidity", "pH", "alcohol", "quality")], 4)
```


--- .class #id

## Red Wine

```{r, echo = FALSE, eval = TRUE}
wine <- read.csv('winequality-red.csv', header = TRUE, sep = ";")
hist(wine$quality, col = "salmon", main = "Red Wine Quality", xlab = "Quality")
```

--- .class #id

## White Wine

```{r, echo = FALSE, eval = TRUE}
wine <- read.csv('winequality-white.csv', header = TRUE, sep = ";")
hist(wine$quality, col = "salmon", main = "White Wine Quality", xlab = "Quality")
```



